In Chapter 2,
the $\alpha$--function is studied, introduced in~\cite{our-vzms-2018}:
\begin{equation}
	\alpha(x) = \varlimsup_{i\to\infty} \max_{i<j\leqslant 2i} |x_i - x_j|
	.
\end{equation}
Since $\alpha(c)=0$,
the $\alpha$--function can also be considered the <<measure of non-convergence>> of a sequence;
equality $\alpha(x) = 0$, however, does not guarantee convergence at all.

It is established that the $\alpha$--function is not shift-invariant with respect to the shift operator $T$,
and an estimate on $\alpha(T^n x)$ is given.
On the other hand, the $\alpha$--function, unlike some Banach limits
\cite{Semenov2010invariant,semenov2011structure},
is invariant with respect to dilation operators $\sigma_n$.
Then, the connection between the $\alpha$--function, the distance from a given sequence to the space $c$
and almost convergence is revealed.
Other properties of the $\alpha$--function are also considered.
We present the main results.

\reflectcorollary{thm:est_alpha_Tn_x_full}
	For any $x\in\ell_\infty$ and $n \in \N$
	\begin{equation}\label{est_alpha_Tn_x}
		\frac{1}{2}\alpha(x) \leq \alpha(T^n x) \leq \alpha(x)
		.
	\end{equation}

\reflecttheorem{thm:alpha_beta_T_seq}
	Let $\beta_k$~--- a monotonically nonincreasing sequence,
	$\beta_k \to \beta$, $\beta\in\left[\frac{1}{2}; 1\right]$, $\beta_1 \leq 1$.
	Then there exists such an $x\in\ell_\infty$ that for any natural $n$
	\begin{equation}
		\frac{\alpha(T^n x)}{\alpha(x)} = \beta_n.
	\end{equation}

\reflecttheorem{thm:alpha_sigma_n}
	For any $x\in\ell_\infty$ and any natural $n$ the equality holds
	\begin{equation}
		\alpha(\sigma_n x) = \alpha(x)
		.
	\end{equation}

\reflecttheorem{thm:alpha_sigma_1_n}
	For any $n\in\N$ and any $x\in\ell_\infty$ it holds
	\begin{equation}
		\alpha(\sigma_{1/n} x) \leq \left( 2- \frac{1}{n} \right) \alpha(x)
		.
	\end{equation}

\reflecttheorem{thm:alpha_Cx_no_gamma}
	The equality holds
	\begin{equation}
		\sup_{x\in\ell_\infty, \alpha(x)\neq 0} \frac{\alpha(Cx)}{\alpha(x)}=1
		.
	\end{equation}

\reflecttheorem{thm:alpha_xy}
	Let $(x\cdot y)_k = x_k\cdot y_k$.
	Then
	$\alpha(x\cdot y)\leq \alpha(x)\cdot \|y\|_* + \alpha(y)\cdot \|x\|_*$,
	where
	\begin{equation}
		\|x\|_* = \limsup_{k\to\infty} |x_k|
	\end{equation}
	is the quotient-norm by $c_0$ on the space $\ell_\infty$.

In paragraph~\ref{sec:space_A0}, the space $A_0 = \{x: \alpha(x) = 0\}$ is discussed.
This space is non-separable, closed under coordinatewise multiplication,
left and right shift operators, Cesàro operator,
dilation operators $\sigma_n$, and averaging contraction $\sigma_{1/n}$.

In paragraph~\ref{sec:noncomplementarity}, it is established that both embeddings
\begin{equation}
	c_0 \subset A_0 \subset \ell_\infty
\end{equation}
are non-complemented.
