
\input vmj.tex

%\usepackage{amssymb,amsfonts,amsmath,mathtext,enumerate,float,amsthm} %подключаем нужные пакеты расширений
%\usepackage{cite}

\Russian

 \def\endpage{??}




 \let\thefootnote\relax\setcounter{section}{0}\setcounter{equation}{0}


 \UDC{ 517.982.276 } %УДК статьи
 \DOI{ } %заполняется редакцией



 \Title{On certain non-complemented embeddings of the space of null sequences}

 \shorttitle{On certain non-complemented embeddings ...}

 \begin{center}
	This work was carried out at Voronezh State University and supported by the BASIS
	Foundation grant 22-7-2-27.
 \end{center}


 \begin{center}
 {Н.~Н.~Авдеев$^{1}$\\[4pt]}
 {\rm\footnotesize{$^1$\,
 Воронежский государственный университет\\
 Россия, 394006, Воронеж, Университетская пл., 1\\
 E-mail: avdeev@math.vsu.ru, nickkolok@mail.ru}}
 \end{center}


\Abstract{
	We study complementability of several subspaces of bounded sequences.
	In particular,
	we prove that the subspace of null sequences $c_0$
	is not complemented in the space $ac_0$ of sequences that almost converge to zero.
}

\Abstract{
	В статье изучается вопрос о дополняемости вложений некоторых подпространств пространства ограниченных последовательностей.
	В частности, доказывается, что недополняемо вложение пространства $c_0$
	сходящихся к нулю последовательностей
	в пространство $ac_0$ почти сходящихся к нулю последовательностей.
}


 {\hangindent17pt\hangafter=0\noindent\footnotesize{\bf Keywords:}
	Banach limits,
	bounded sequence,
	almost convergent sequence,
	convergent sequence,
	non-complemented subspace
 \par} %ключевые слова

 {\hangindent17pt\hangafter=0\noindent\footnotesize{\bf Ключевые слова:}
	банахов предел,
	ограниченная последовательность,
	почти сходящаяся последовательность,
	сходящаяся последовательность,
	недополняемое подпространство
 \par} %ключевые слова



 \smallskip

 {\hangindent17pt\hangafter=0\noindent\footnotesize {\bf Mathematical Subject Classification (2000):}  46B45 \par} %математические классификаторы



\section{Introduction}

Let $\ell_\infty$ be the space of all bounded sequences
endowed with the usual norm
\begin{equation}
	\|x\| = \sup_{n\in\mathbb{N}} |x_n|
	,
\end{equation}
where $\mathbb{N}$ denotes set of all positive integers,
and let $c_0$ be the subspace  of null-sequences.
The famous result of Phillips~\cite{phillips1940linear}
states that $c_0$ is not complemented in $\ell_\infty$.
This statement holds due to the following result~\cite{phillips1940linear} :

\begin{theorem}
	\label{thm:phillips}
	There is no bounded linear operator $P: \ell_\infty \to c_0$ such that for every
	$x \in c_0$ the equality $Px =x$ holds.
\end{theorem}

Theorem~\ref{thm:phillips} gives the very first example of a non-complemented subspace.
Later, more such subspaces were found;
for further discussion we refer the reader to~\cite[2.c--2.f]{lindenstrauss1977classical}.

The notion of almost convergence is a generalization of the notion of convergence.
Before we proceed to it, we need to introduce the concept of Banach limits,
which (expectably) provides a way to generalize the concept of the limit.

\begin{definition}
	A linear functional $B\in\ell_\infty^*$ is said to be a \emph{Banach limit} if
	\begin{enumerate}[label=(\roman*)]
		\item
			$B\geq0$, that is $Bx \geq 0$ for $x \geq 0$,
		\item
			$B\mathbb{I}=1$, where $\mathbb{I} =(1,1,\ldots)$,
		\item
			$B(Tx)=B(x)$ for $x\in \ell_\infty$,
			where $T$ is the shift operator $T(x_1,x_2,\ldots)=(x_2,x_3,\ldots)$.
	\end{enumerate}
\end{definition}
The set of all Banach limits is denoted by $\mathfrak{B}$.
The existence of Banach limits was announced by Mazur~\cite{Mazur} and proved by Banach~\cite{banach1993theorie}.
There are infinitely many Banach limits.
Nevertheless, there exist such sequences that all Banach limits agree on them.
The following definition is due to Lorentz~\cite{lorentz1948contribution}.

\begin{definition}
	A sequence $x\in \ell_\infty$ is said to be \emph{almost convergent} to $t\in \mathbb{R}$
	if for every $B\in\mathfrak{B}$ the equality
	\begin{equation}
		Bx = t
	\end{equation}
	holds.
\end{definition}
The set of all sequences that are almost convergent to $t$ is denoted by $ac_t$;
the space of all almost convergent sequences is denoted by $ac$.
Lorentz proved the following criterion of almost convergence~\cite{lorentz1948contribution}:

\begin{theorem}
	A sequence $x=(x_1,x_2,...)$ is almost convergent to $t\in\mathbb{R}$ iff
	\begin{equation}
		\label{eq:crit_Lorentz}
		\lim_{n\to\infty} \frac{1}{n} \sum_{k=m+1}^{m+n} x_k = t
	\end{equation}
	uniformly by $m\in\mathbb{N}$.
\end{theorem}

It's easy to see that $c_0 \subset ac_0$ and that the inclusion is proper.
Alekhno gave an elegant proof~\cite[Theorem 8]{alekhno2006propertiesII}
that $ac_0$ is not complemented in $\ell_\infty$.
The proof is based on the original Phillips's proof of Theorem~\ref{thm:phillips}
and uses some lemmas from there.
For more details on Banach limits and almost convergence we refer the reader to~\cite{sucheston1967banach,Eberlein,semenov2020geomBL}.

In Section~\ref{sec:c0_in_ac0} of the present article, we prove that $c_0$ is not complemented in $ac_0$.
So, all the three inclusions
\begin{equation}
	c_0 \subset \ell_\infty,
	\quad
	ac_0 \subset \ell_\infty,
	\quad\mbox{and}\quad
	c_0 \subset ac_0,
\end{equation}
are not complemented.
Our proof is inspired by Whitley's approach~\cite{whitley1968projecting}
and the discussion~\cite{mathSE_Phillips}.

In Sections~\ref{sec:A0_in_ell_infty} and~\ref{sec:c0_in_A0}
we proceed with applying the same approach to the inclusion chain $c_0 \subset A_0 \subset \ell_\infty$,
where
\begin{equation}
	A_0 = \{x\in\ell_\infty: \alpha(x) = 0\}
	,
\end{equation}
\begin{equation}
	\alpha(x) = \varlimsup_{i\to\infty} \max_{i<j\leqslant 2i} |x_i - x_j|
	.
\end{equation}

The function $\alpha(x)$, first introduced in~\cite{our-vzms-2018},
may be considered as a way to characterize \emph{how much non-Cauchy a given bounded sequence is}.
Note that the condition $\alpha(x) =0$ is weaker than the Cauchy condition.

It has turned out that the functional $\alpha(x)$ is closely related to the theory of Banach limits.
In particular, the equality $A_0\cap ac_0 = c_0$ holds~\cite{avdeev2019space}.
In~\cite{our-ped-2018-alpha-Tx} it is shown that the set $A_0$ is shift-invariant, that is
$TA_0 = A_0$ despite the fact that for some $x\in\ell_\infty$
one has $\alpha(Tx)<\alpha(x)$.
For further investigation of $\alpha(x)$ we also refer the reader to~\cite{avdeev2021subsets}.

\section{The subspace $c_0$ is not complemented in $ac_0$}
\label{sec:c0_in_ac0}

The following lemma is a classical result, and we prove it for the sake of completeness.
\begin{lemma}
	\label{lem:uncountable_subsets_of_N_with_finite_intersections}
	There exists an uncountable family of subsets
	$\{S_i\}_{i\in I}$, $S_i \subset \mathbb{N}$,
	such that each $S_i$ is countable and for every $i\neq j$ the intersection $S_i \cap S_j$ is finite.
\end{lemma}

\begin{proof}
	Consider a bijection $\mathbb{N} \leftrightarrow \mathbb{Q}$
	and let $I = \mathbb{R}$.
	For $i\in I$ we set $S_i = \{q_n\}$,
	where $\{q_n\} \subset \mathbb{Q}$ is a sequence which converges monotonically to $i$.
\end{proof}








The following lemma is inspired by~\cite{mathSE_Phillips}.

\begin{lemma}
	\label{lem:c_0_not_complemented_in_ac_0}
	For each linear operator $Q: ac_0 \to ac_0$ such that $c_0\subseteq \ker Q$,
	there exists infinite subset $S \subset \mathbb{N}$ such that
	\begin{equation}
		\forall(x \in ac_0 : \supp x \subset S)[Qx = 0]
		.
	\end{equation}
\end{lemma}



\begin{proof}
	Notice first that for any infinite subset $S \subset \mathbb{N}$
	there exists $x\in ac_0\setminus c_0$ with $\supp x \subseteq S$.
	Indeed, we can find such $x$ with $0 < x \leq \chi_S$
	that contains infinitely many ones, and the distance between the ones
	is enough for Lorentz's criterion~\eqref{eq:crit_Lorentz} to be hold.



	Let $\{S_i\}_{i \in I}$ be a family of subsets of $\mathbb{N}$
	that satisfy the conditions of Lemma~\ref{lem:uncountable_subsets_of_N_with_finite_intersections}.
	Suppose to the contrary that
	\begin{equation}
		\forall(\mbox{infinite }S\subset\mathbb{N})\exists(x \in ac_0 : \supp x \subset S)[Qx \neq 0]
		.
	\end{equation}
	In particular,
	\begin{equation}
		\forall(i\in I)\exists(x_i \in ac_0 : \supp x_i \subset S_i)[Q(x_i) \neq 0]
		.
	\end{equation}

	Note that $x_i \notin c_0$ because $c_0\subseteq \ker Q$.
	Without loss of generality we can assume that $\|x_i\|=1$ for all $i \in I$.

	Consider $I_n = \{i \in I\,:\,(Qx_i)_n \neq 0\}$,
	then $I = \bigcup\limits_{n\in\mathbb{N}} I_n$.
	Thus, we can find $n$ such that $I_n$ is also uncountable
	(otherwise $I$ would be countable as a countable union of countable sets,
	which contradicts to conditions of Lemma~\ref{lem:uncountable_subsets_of_N_with_finite_intersections}).

	Сonsider now $I_{n,k} = \{i \in I_n\,:\,|(Qx_i)_n| \geq 1/k\}$,
	then $I_n = \bigcup\limits_{k\in\mathbb{N}} I_{n,k}$.
	Applying the same argument as above, one can easily see that the set $I_{n,k}$ is uncountable for some $k$.
	Let us choose such $I_{n,k}$ and proceed with it.

	So, we have an uncountable set $I_{n,k}$ and
	\begin{equation}
		\forall(i\in I_{n,k})\exists(x_i \in ac_0 : \supp x_i \subset S_i)\Bigl[\|x_i\|=1 \mbox{~~and~~} |(Qx_i)_n| \geq 1/k\Bigr]
		.
	\end{equation}

	Consider a finite set $J \subset I_{n,k}$ with $\#J>1$
	(here $\#J$ stands for the cardinality of the set $J$).
	Take
	\begin{equation}
		y = \sum_{j \in J} \operatorname{sign}{(Qx_j)_n} \cdot x_j
		.
	\end{equation}
	Since the intersection $S_i \cap S_j$ is finite for any $i \neq j$ and
	$\supp x_j \subset S_j$,
	the intersection $\bigcap\limits_{j\in J} \supp x_j$ is also finite.
	Hence, $y = f + z$,
	where $\supp f$ is finite and $\|z\| \leq 1$.

	On the other hand,
	\begin{equation}
		\label{eq:non_complemented_sum_cardinality}
		(Qy)_n = \sum_{j \in J}
		(\operatorname{sign}(Qx_j)_n)
		\cdot (Qx_j)_n \geq \frac{\# J}{k}
		.
	\end{equation}
	Note, that $f\in c_0$ and we have $Qf = 0$, because $c_0 \subseteq \ker Q$.
	Thus, $Qy = Q(f+z) = Qf + Qz = Qz$ and
	\begin{equation}
		\label{eq:norm_Q_estimate}
		\frac{\# J}{k} \leq (Qy)_n \leq \|Qy\| = \|Qz\| \leq \|Q\| \cdot \|z\| \leq \|Q\|
		.
	\end{equation}
	Due to~\eqref{eq:norm_Q_estimate}, we obtain $\# J \leq \|Q\| k$ for every $J\subset I_{n,k}$.
	This contradicts the fact that $I_{n,k}$ is uncountable,
	and we are done.
\end{proof}

\begin{theorem}
	The subspace $c_0$ is not complemented in $ac_0$.
\end{theorem}

\begin{proof}
	Suppose to the contrary that
	there exists a continuous projection $P: ac_0 \to c_0$.
	Applying Lemma~\ref{lem:c_0_not_complemented_in_ac_0} to $I-P$
	we can find infinite subset $S\subset\mathbb{N}$
	such that $\forall(x\in ac_0 : \supp x \subset S)[(I-P)x = 0]$
	(such $x \in ac_0 \setminus c_0$ exists even if $\chi_S \notin ac_0$).
	But then $Px\notin c_0$,
	which contradicts the fact that $P$ is a projection onto $c_0$.
\end{proof}





\section{The subspace $A_0$ is not complemented in $\ell_\infty$}
\label{sec:A0_in_ell_infty}



\begin{lemma}
	\label{lem:c_0_not_complemented}
	For each linear operator $Q: \ell_\infty \to \ell_{\infty}$ such that $c_0\subseteq \ker Q$,
	there exists infinite subset $S \subset \mathbb{N}$ such that
	\begin{equation}
		\forall(x \in \ell_\infty : \supp x \subset S)[Qx = 0]
		.
	\end{equation}
\end{lemma}

\begin{proof}
	Let $\{S_i\}_{i \in I}$ be a family of subsets of $\mathbb{N}$
	such that conditions of Lemma~\ref{lem:uncountable_subsets_of_N_with_finite_intersections} are hold.
	Suppose to the contrary that
	\begin{equation}
		\forall(\mbox{infinite }S\subset\mathbb{N})\exists(x \in \ell_\infty : \supp x \subset S)[Qx \neq 0]
		.
	\end{equation}
	In particular,
	\begin{equation}
		\forall(i\in I)\exists(x_i \in \ell_\infty : \supp x_i \subset S_i)[Q(x_i) \neq 0]
		.
	\end{equation}
	The rest of the proof is similar to that of Lemma~\ref{lem:c_0_not_complemented_in_ac_0}.
\end{proof}





\begin{theorem}
	The subspace $A_0$ is not complemented in $\ell_\infty$.
\end{theorem}

\begin{proof}
	Suppose to the contrary that
	there exists a continuous projection $P: \ell_\infty \to A_0$.
	Then $c_0\subset A_0\subset\ker (I-P)$.
	Applying Lemma~\ref{lem:c_0_not_complemented} to $I-P$
	we can find infinite subset $S\subset\mathbb{N}$
	such that $\forall(x\in\ell_\infty : \supp x \subset S)[(I-P)x = 0]$.
	Let $S' \subset S$ be such that $\chi_S$ contains
	infinite quantities of both ones and zeros.
	But then $\alpha(P\chi_{S'}) = \alpha(\chi_{S'}) = 1$ and $P\chi_{S'} \notin A_0$,
	which contradicts the fact  that $P$ is a projection onto $A_0$.
\end{proof}



\section{The subspace $c_0$ is not complemented in $A_0$}
\label{sec:c0_in_A0}

To prove the fact, we need some auxiliary constructions from~\cite{our-vzms-2018}.


Let us define linear operator $F:\ell_\infty \to \ell_\infty$ as following:
\begin{equation}
	\label{operator_F}
	(Fy)_k = y_{i+2}, \mbox{ for } 2^i < k \leq 2^i+1
\end{equation}

For example,
$$
	F(\{1,2,3,4,5,6, ...\}) = \{1,2,\,3,3,\,4,4,4,4,\,5,5,5,5,5,5,5,5,\,6...\}
$$


It is easy to see that the equality
\begin{equation}
	\label{eq:alpha_F}
	\alpha(Fx) = \varlimsup_{k\to\infty} |x_{k+1} - x_{k}|
\end{equation}
holds.

Let us also define linear operator $M:\ell_\infty \to \ell_\infty$ as following:
\begin{multline*}
	M(\omega_1,\omega_2,...)=\left(
		0, 1\omega_1,
		0, \frac{1}{2}\omega_2, 1\omega_2, \frac{1}{2}\omega_2,
		0, \frac{1}{3}\omega_3, \frac{2}{3}\omega_3, 1\omega_3, \frac{2}{3}\omega_3, \frac{1}{3}\omega_3,
		0, ...,
	\right. \\ \left.
		0, \frac{1}{p}\omega_p, \frac{2}{p}\omega_p, ..., \frac{p-1}{p}\omega_p, 1\omega_p,
			\frac{p-1}{p}\omega_p, ..., \frac{2}{p}\omega_p, \frac{1}{p}\omega_p,
		0, \frac{1}{p+1}\omega_{p+1}, ...
	\right)
	.
\end{multline*}
Note that due to~\eqref{eq:alpha_F} we have $FM: \ell_\infty \to A_0$.


\begin{lemma}
	\label{lem:c_0_not_complemented_in_A_0}
	For each linear operator $Q: A_0 \to A_0$ such that $c_0\subseteq \ker Q$,
	there exists infinite subset $S \subset \mathbb{N}$ such that
	\begin{equation}
		\forall(x \in A_0 : \supp x \subset S)[Qx = 0]
	\end{equation}
	and $x\in A_0\setminus c_0$ such that $\supp x \subseteq S$.
\end{lemma}

\begin{proof}
	Let $\{U_i\}_{i \in I}$ be a family of subsets of $\mathbb{N}$
	such that conditions of Lemma~\ref{lem:uncountable_subsets_of_N_with_finite_intersections} are hold.
	Let $\{S_i\}_{i \in I}$ be a family of subsets of $\mathbb{N}$
	defined by the equality $S_i = \supp FM\chi_{U_i}$.
	Obviously, the family of sets $\{S_i\}_{i \in I}$ also
	satisfies the conditions of Lemma~\ref{lem:uncountable_subsets_of_N_with_finite_intersections}.
	Moreover, for every $i\in I$ we have $x = FM\chi_{U_i} \in A_0\setminus c_0$.

	Suppose to the contrary that
	\begin{equation}
		\forall(\mbox{infinite }S\subset\mathbb{N})\exists(x \in A_0 : \supp x \subset S)[Qx \neq 0]
		.
	\end{equation}
	In particular,
	\begin{equation}
		\forall(i\in I)\exists(x_i \in A_0 : \supp x_i \subset S_i)[Q(x_i) \neq 0]
		.
	\end{equation}
	The rest of the proof is similar to that of Lemma~\ref{lem:c_0_not_complemented_in_ac_0}.

\end{proof}

\begin{theorem}
	The subspace $c_0$ is not complemented in $A_0$.
\end{theorem}

\begin{proof}
	Suppose to the contrary that
	there exists a continuous projection $P: A_0 \to c_0$.
	Applying Lemma~\ref{lem:c_0_not_complemented_in_A_0} to $I-P$
	we can find infinite subset $S\subset\mathbb{N}$
	such that $\forall(x\in A_0 : \supp x \subset S)[(I-P)x = 0]$,
	and $x\in A_0 \setminus c_0$ such that $\supp x \subseteq S$.
	But then $Px = x\notin c_0$,
	which contradicts  the fact  that $P$ is a projection onto $c_0$.
\end{proof}


\section{Acknowledgements}
Author thanks Dr. Prof. E.M. Semenov and Dr. A.S. Usachev for encouragement and discussions.


%\printbibliography
%\printbibitembibliography


\begin{thebibliography}{99}
%
\bibitem{phillips1940linear}
\emph{Phillips R. S.} On linear transformations // Transactions of the
American Mathematical Society. — 1940. — Vol. 48, no. 3. — Pp. 516–541.
%
\bibitem{lindenstrauss1977classical}
\emph{Lindenstrauss J., Tzafriri L.}
 Classical Banach spaces I: Sequence Spaces. – 1977. – Vol. 92.

\bibitem{Mazur}
\emph{Mazur S.} O metodach sumowalno\'{s}ci // Ann. Soc. Polon.
Math. (Supplement). — 1929. — Pp. 102–107.
%
\bibitem{banach1993theorie}
\emph{Банах С.} Теория линейных операций. — Регуляр. и
хаот. динамика. — М., 2001.
%
\bibitem{lorentz1948contribution}
\emph{Lorentz G. G.} A contribution to the theory of divergent
sequences // Acta Mathematica. — 1948. — Vol. 80, no. 1. — Pp. 167–190. —
ISSN 0001-5962.
%
\bibitem{alekhno2006propertiesII}
\emph{Алехно Е.} Некоторые специальные свойства функционалов
Мазура. II // Аналитические методы анализа и дифференциальных
уравнений. Vol. 2. — Труды Института математики НАН Беларуси, 2006. —
С. 17–23.
%
\bibitem{sucheston1967banach}
\emph{Sucheston L.} Banach limits // Amer. Math. Monthly. —
1967. — Vol. 74. — Pp. 308–311. — ISSN 0002-9890.
%
\bibitem{Eberlein}
\emph{Eberlein W. F.} Banach-{H}ausdorff limits // Proc. Amer.
Math. Soc. — 1950. — Vol. 1. — Pp. 662–665. — ISSN 0002-9939.
%
\bibitem{semenov2020geomBL}
\emph{Семёнов Е. М.}, \emph{Сукочев Ф. А.},
\emph{Усачев А. С.} Геометрия банаховых пределов и их
приложения // Успехи математических наук. — 2020. — Vol. 75, 4 (454). —
Pp. 153–194.
%
\bibitem{whitley1968projecting}
\emph{Whitley R.} Projecting $m$ onto $c_0$ // The American
Mathematical Monthly. — 1966. — Vol. 73, no. 3. — Pp. 285–286.
%
\bibitem{mathSE_Phillips}
Why doesn’t $c_0$ admit a complement in $\ell _\infty $? — URL: \url
{https://math.stackexchange.com/questions/2467426}
%
\bibitem{our-vzms-2018}
\emph{Авдеев Н. Н.}, \emph{Семенов Е. М.} Об
асимптотических свойствах оператора Чезаро // Воронежская Зимняя
Математическая школа С.Г. Крейна – 2018. Материалы Международной
конференции. Под ред. В.А. Костина. — 2018. — С. 107–109.
%
\bibitem{avdeev2019space}
\emph{Avdeev N.} On the Space of Almost Convergent Sequences //
Mathematical Notes. — 2019. — Vol. 105, no. 3/4. — Pp. 464–468. — URL: \url
{https://www.scopus.com/record/display.uri?origin=inward&eid=2-s2.0-85065492318}
%
\bibitem{our-ped-2018-alpha-Tx}\emph{Авдеев Н. Н.} О суперпозиции оператора сдвига и одной
функции на пространстве ограниченных последовательностей // Некоторые
вопросы анализа, алгебры, геометрии и математического образования. —
2018. — C. 20–21.
%
\bibitem{avdeev2021subsets}
\emph{Avdeev N.} On Subsets of the Space of Bounded Sequences //
Mathematical Notes. — 2021. — Vol. 109, no. 1. — Pp. 150–154.
\end{thebibliography}



\begin{thebibliography}{99}
%
\bibitem{phillips1940linear}
Phillips R. S. On linear transformations //
\emph{Transactions of the American Mathematical Society.}
— 1940. — Vol. 48, no. 3. — Pp. 516–541.
%
\bibitem{lindenstrauss1977classical}
Lindenstrauss J., Tzafriri L.
\emph{Classical Banach spaces I: Sequence Spaces.} – 1977. – Vol. 92.

\bibitem{Mazur}
Mazur S. O metodach sumowalno\'{s}ci //
\emph{Ann. Soc. Polon. Math. (Supplement).}
 — 1929. — Pp. 102–107.
%
\bibitem{banach1993theorie}
Banach S.
\emph{Th\'{e}orie des op\'{e}rations lin\'{e}aires.} — Sceaux :
\'{E}ditions Jacques Gabay, 1993. — Pp. iv+128. — ISBN 2-87647-148-5. — Reprint
of the 1932 original.
%
\bibitem{lorentz1948contribution}
Lorentz G. G.
A contribution to the theory of divergent sequences // \emph{Acta Mathematica.}
— 1948. — Vol. 80, no. 1. — Pp. 167–190. —
ISSN 0001-5962.
%
\bibitem{alekhno2006propertiesII}
Alekhno E. Some special properties of Mazur functionals II //
\emph{Analytical Methods of Analysis and Differential Equations, vol 2.}
 — Proceedings of Mathematics Institute of Belarus National Academy of Science, 2006. —
Pp. 17–23.
(in Russian)
%
\bibitem{sucheston1967banach}
Sucheston L. Banach limits //
\emph{Amer. Math. Monthly.} —
1967. — Vol. 74. — Pp. 308–311. — ISSN 0002-9890.
%
\bibitem{Eberlein}
Eberlein W. F. Banach-{H}ausdorff limits //
\emph{Proc. Amer. Math. Soc.} — 1950. — Vol. 1. — Pp. 662–665. — ISSN 0002-9939.
%
\bibitem{semenov2020geomBL}
Semenov E. M. , Sukochev F. A. , Usachev A. S.
Geometry of Banach limits and their applications
//
\emph{Russian Mathematical Surveys.} — 2020. — Vol. 75:4. —
Pp. 725–763.
%
\bibitem{whitley1968projecting}
Whitley R.
Projecting $m$ onto $c_0$ //
\emph{The American Mathematical Monthly.} — 1966. — Vol. 73, no. 3. — Pp. 285–286.
%
\bibitem{mathSE_Phillips}
Why doesn’t $c_0$ admit a complement in $\ell _\infty $? — URL: \url
{https://math.stackexchange.com/questions/2467426}
%
\bibitem{our-vzms-2018}
Avdeev N. N., Semenov E. M.
On asymptotic properties of Cesaro operator
//
\emph{Voronezhskaya Zimnyaya Matematicheskaya shkola S.G. Kreyna – 2018. Materialy Mezhdunarodnoy konferentsii.}
[Proc. of Voronezh Intl. Winter Math. School named after S.G. Kreyn].
Voronezh, 2018, pp. 107–109. (in Russian)
%
\bibitem{avdeev2019space}
\emph{Avdeev N.} On the Space of Almost Convergent Sequences //
Mathematical Notes. — 2019. — Vol. 105, no. 3/4. — Pp. 464–468. — URL: \url
{https://www.scopus.com/record/display.uri?origin=inward&eid=2-s2.0-85065492318}
%
\bibitem{our-ped-2018-alpha-Tx}
Avdeev N. N.
On superposition of shift operator and one function on the space of bounded sequences
//
\emph{Nekotorye voprosy analiza, algebry, geometrii i matematicheskogo obrazovaniya.}
[Some qiestions of analysis, algebra, geometry and mathematical education].
Voronezh, 2018, pp. 20–21.
(in Russian)
%
\bibitem{avdeev2021subsets}
Avdeev N. On Subsets of the Space of Bounded Sequences //
\emph{Mathematical Notes.} — 2021. — Vol. 109, no. 1. — Pp. 150–154.

\end{thebibliography}



 %оформление параграфов
 \section{N. Название параграфа}


 %оформление теорем
 \Teorema{ 1 {\rm (название теоремы при наличии)}}
 %текст теоремы
 \Endproc


 %оформление доказательства
 \beginproof
 %текст доказательства
 \endproof


 %оформление леммы
 \Lema{ 1}
 %текст леммы
 \Endproc


 %оформление следствия
 \Sledstvie{}
 %текст следствия
 \Endproc

 %оформление замечания
 \Zam{}
 %текст замечания

 %оформление примера
 \Primer{}
 %текст примера




%%%% Список литературы на рус. яз.

% При наличии DOI обязательно указывать!!!

\Lit

 \begin{enumerate}
 {\footnotesize
 \itemsep=0pt
 \parskip=0pt


 \bib{Канторович Л.~В., Акилов Г.~П.}
 {Функциональный анализ.---М.: Наука,  1984.---750~с.} %ссылка на книгу

 \bib{Рябых~В.~Г.}
 {Приближение неаналитических функций аналитическими~/\!/ Мат. сб.---2006.---Т.~191, \No~2.---С.~87--94.}%ссылка на журнал

 \bib{Дурдиев Д.~К., Тотиева Ж.~Д.}
 Задача об определении одномерного ядра электровязкоупругости~/\!/
 Сиб. мат. журн.---2017.---Т.~58, \No~3.---С.~553--572. DOI: 10.17377/smzh.2017.58.307. %ссылка на журнал

 \bib{Бурчаев Х.~Х., Рябых В.~Г., Рябых Г.~Ю.}
 {Некоторые свойства экстремальных функций линейных функционалов над пространствами Харди и Бергмана~/\!/
 Мат. форум. Т. 9. Исслед. по мат. анализу, дифференц. уравнениям и мат.
 моделированию.---Владикавказ: ЮМИ ВНЦ РАН, 2015.---С.~125--139.---(Итоги науки. Юг России).} %ссылка на сборник трудов

 }
 \end{enumerate}



 \Address{\textit{Статья поступила  чч.мм.гггг.}\\[4pt]  % заполняется редакцией
 \textsc{ФИО полностью}\\
 место работы,\\
 \textsl{должность}\\
 полный адрес места работы\\
 E-mail:
 \par}




 \newpage

 % Заполняем данные на английском языке!


 \bigskip
 \begin{center}
 НАЗВАНИЕ СТАТЬИ НА АНГЛ. ЯЗ. (заглавными буквами)
 \end{center}


 \begin{center}
 Фамилия, И.~О. на англ. яз.$^{1}$\\[4pt]
 {\rm\footnotesize{$^1$\,
 место работы  на англ. яз.\\
 полный адрес места работы на англ. яз.\\
 E-mail: }}
 \end{center}



 {\hangindent0pt\hangafter=0\footnotesize{\textbf{Abstract.} Аннотация на англ. яз.
 \par}

 {\hangindent0pt\hangafter=0\footnotesize{\bf Key words:}~ключевые слова на англ. яз.
 \par}



%%%% Список литературы на англ. яз.

% При наличии DOI обязательно указывать!!!

% Указывать переводную версию статьи, книги, сборника при наличии!


 \Refer

 \begin{enumerate}
 {\footnotesize
 \itemsep=0pt
 \parskip=0pt

 \bib{Kantorovich, L.~V. and Akilov, G.~P.}
 {\it Funktsional'nyy Analliz} [Functional Analysis],
 Moscow,
 Nauka,
 1984,
 750~p.
 (in Russian).


 \bib{Ryabykh, V.~G.}
 Approximation of non-analytic functions by analytic functions.
 {\it Sbornik: Mathematics},
 2006,
 vol. 197,
 no. 2,
 pp. 225--233.


 \bib{Durdiev, D.~K. and Totieva, Zh.~D.} The Problem of Finding the One-Dimensional Kernel of the Thermoviscoelasticity Equation,
 \textit{Mathematical Notes},
 2018,
 vol.~103,
 no.~1--2,
 p.~118--132.
 DOI: 10.1134/S0001434618010145.


 \bib{Burchaev, Kh.~Kh., Ryabykh, V.~G. and Ryabykh, G.~Yu.}
 Some properties of the extremal functions of linear functionals on Hardy and Bergman spaces.
 \textit{Mat. Forum. T. 9. Issledovaniya po Matematicheskomu Analizu, Differentsialnym Uravneniyam i Matematicheskomu Modelirovaniyu $($Itogi Nauki. Yug Rossii$)$}
 [Math. Forum. Vol. 9. Studies in Mathematical Analysis, Differential Equations, and Mathematical Modeling (Review of Science: The South of Russia)],
 Vladikavkaz, SMI VSC RAS,
 2015,
 pp.~125--139
 (in Russian).

}
\end{enumerate}




 \Address{\textit{Received  }\\[4pt] % заполняется редакцией
 \textsc{ФИО полностью на англ. яз.}\\
 место работы  на англ. яз.,\\
 полный адрес места работы на англ. яз.,\\
 \textsl{Должность на англ. яз.}\\
 E-mail:
 \par}


\end{document}
